---
title: "Tidy Tuesday Demo - Tate Art"
author: "Ludmila Janda"
date: "1/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load package and data, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(scales)

tuesdata <- tidytuesdayR::tt_load(2021, week = 3)
artwork <- tuesdata$artwork
artists <- tuesdata$artists
```


# Join artwork and artist datasets
```{r left join}
art_artists <- left_join(artwork, artists, by = c("artistId" = "id"))
```


# Create new variable that is the area of the art 
```{r}
art_artists$area <- art_artists$height * art_artists$width
```


# Graph art size in relation to gender - boxplot
```{r}
art_artists %>% 
ggplot(aes(area, gender)) + 
  geom_boxplot() + 
  scale_x_continuous(labels = comma) +
  theme_minimal() + 
  labs(y = NULL, x = "Area", 
       title = "Who Makes Bigger Art") 
```

# Remove outliers
```{r}
summary(art_artists$area)
121706 + (IQR(art_artists$area, na.rm = TRUE) * 1.5)
```

# Graph art size in relation to gender - boxplot
```{r}
art_artists %>% 
    filter(area < 278463.5, 
         !is.na(gender)) %>% 
  ggplot(aes(area, gender)) + 
  geom_boxplot() + 
  scale_x_continuous(labels = comma) +
  theme_minimal() + 
  labs(y = NULL, x = "Area", 
       title = "Who Makes Bigger Art") 
```

# Graph art size in relation to gender - ridgeplot
```{r}
library(ggridges)

art_artists %>% 
  filter(area < 278463.5, 
         !is.na(gender), 
         !is.na(year)) %>% 
  mutate(century = (floor(year / 100)) * 100) %>% 
ggplot(aes(x = area, y = gender)) + 
  geom_density_ridges(rel_min_height = 0.01, 
                      jittered_points = TRUE, 
                      position = "raincloud", 
                      alpha = 0.1, scale = 0.5, 
                      quantile_lines = TRUE,
                      quantiles = 2) +
  theme_minimal() + 
  labs(y = NULL, x = "Area") + 
  scale_x_continuous(labels = comma) + 
  labs(y = NULL, x = "Area", 
       title = "Who Makes Bigger Art") 
```
# Graph size of art over time
```{r}
art_artists %>% 
  filter(!is.na(gender)) %>% 
  ggplot(aes(year, area)) + 
  geom_col() + 
  scale_y_continuous(labels = comma) +
  theme_minimal() + 
  labs(y = "Area", x = "Year", 
       title = "Art Area Over Time")
```

# Graph art size in relation to gender and time - ridgeplot
```{r}
art_artists %>% 
  filter(area < 278463.5, 
         !is.na(gender), 
         !is.na(year)) %>% 
  mutate(century = (floor(year / 100)) * 100) %>% 
ggplot(aes(x = area, y = gender)) + 
  geom_density_ridges(rel_min_height = 0.01, 
                      jittered_points = TRUE, 
                      position = "raincloud", 
                      alpha = 0.1, scale = 0.5, 
                      quantile_lines = TRUE,
                      quantiles = 2) +
  facet_wrap(~century) +
  theme_minimal() + 
  labs(y = NULL, x = "Area") + 
  scale_x_continuous(labels = comma) + 
  labs(y = NULL, x = "Area", 
       title = "Who Makes Bigger Art by Century") 
```



# Quick and dirty regression
```{r}
a <- lm(area ~ gender + year, art_artists)
summary(a)
```


# Quick and dirty regression with gender * year interaction
```{r}
a <- lm(area ~ gender + year + gender * year, art_artists)
summary(a)
```


# Turner effect?
```{r}
t <- art_artists %>% mutate(turner = ifelse(artist == "Turner, Joseph Mallord William", 1, 0))
a <- lm(area ~ gender + year + gender * year + turner, t)
summary(a)
```

